\documentclass[11pt]{amsart}

\usepackage{a4wide}
\usepackage{paralist}
\usepackage{url}

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cS}{\mathcal{S}}

\begin{document}
\begin{center}
\textbf{\sffamily
   Discrete and Algorithmic Geometry }

\medskip
   Julian Pfeifle,
   UPC, 2018
\end{center}

\bigskip

\begin{center}
  \textbf{\sffamily Participants}
\end{center}

\medskip

\section*{Your name here}
(your github login)

Tell us what type of math you have studied so far, where you did that, what you would like to learn from this course, what passions you have for the future, and anything else about you that you'd like to share

\medskip

\section*{Víctor Ruiz Herrero}
(rufyzos)

I  have  studied  maths  in  FME,  I  would  like  to  learn  a  lot  of  geometry  in  this course and in the future I would like to be a doctor in Mathematics.

\medskip

<<<<<<< HEAD
\section*{Xavier Gombau Pascual}
(xavi-gombau)

I have studied a degree in Telecommunications Engineering for the last 4 years here in Barcelona, at UPC. This course, I would like to study computation-related topics and code a little bit! I'm not sure what to do in a near future, but I have some ideas as an entrepreneur. Looking forward to enjoy this course! 
=======
\section*{Esteve Tarrago Sanchis}
(tarragoesteve)

I  studied computer science and industrial engineering at UPC. There we study some discrete and applied math. I would like to learn more about geometry, and in particular those structures useful to model real-world. One topic that I may focus on the future is reinforcement learning applied on to robots policies. 

\section*{Diego Acedo Moscoso}
(diegoacedo)

I studied a Degree in Mathematics in the University of Cadiz. I am interested mostly in group theory, but I'm also keen on measure theory and algebraic topology, and I do not really dislike many parts of mathematics. I have not learned much geometry before, so I hope with this course I can get some ideas.
I am not sure about my future yet. After finishing this master, I plan to get some job experience, and hopefully some years later I will try to do a Ph.D.


>>>>>>> b52aca5ab101daa0e16a700435beec0148ed5044

\end{document}


